Master's Project Journal

### 2019-04-15 thesis/NetworkImplemenation.tex
diagrams please

with small tweaks to unrelated modules likely to cause Vivado to rearrange the layout of the \ac{RO}s and thus change the centre frequency of a given \ac{DCO}.

>>>>

With the hardware description of the \ac{RO} completed, testing of an instance of the \ac{RO} with a constant control code of zero was attempted, and it was discovered that the estimation of the centre frequency based on the propagation delay was off by $100$s of $\si{\kilo\hertz}$. The addition of 100 inverters was required to restore a centre of $5~\si{\mega\hertz}$. After the \ac{RO} was integrated into \ac{ADPLL} 2 the centre frequency was discovered to have changed once more. The minor variation caused by the now variable control code had changed the average propagation delay through the inverters once more, now requiring 373 inverters for $5~\si{\mega\hertz}$.

When, later in the project, additional \ac{RO}s were implemented to form networks, 373 inverters proved a suitable starting point which consistently delievered \ac{DCO}s with a centre frequency within $200~\si{\kilo\hertz}$ of $5~\si{\mega\hertz}$. For the purposes of describing a typical tuning range, the average propagation delay of an \ac{RO} consisting of 373 inverters with a centre frequency of $5.06~\si{\mega\hertz}$ will be used. To avoid the aforementioned issues with constant control codes, the fixed code was achieved by implementing an \ac{ADPLL} and setting the \ac{PI} filter gains to zero at runtime before performing a reset.
%TODO possibily problematic in the last two paragraphs

%TODO freqs n stuff
